P versus NP

### 2020-01-05 doc/manuscript.tex
Example of disqualification

The $P = NP$ question is also singular in the number of approaches that researchers have brought to bear upon it over the years \cite{DEO10}. From the initial question in logic, the focus moved to complexity theory where early work used diagonalization and relativization techniques \cite{DEO10}. It was showed that these methods were perhaps inadequate to resolve $P$ versus $NP$ by demonstrating relativized worlds in which $P = NP$ and others in which $P \neq NP$ \cite{BA75}. This shifted the focus to methods using circuit complexity and for a while this approach was deemed the one most likely to resolve the question \cite{DEO10}. Once again, a negative result showed that a class of techniques known as $``$Natural Proofs$"$ that subsumed the above could not separate the classes $NP$ and $P$, provided one-way functions exist \cite{RAZ97}. There has been speculation that resolving the $P = NP$ question might be outside the domain of mathematical techniques \cite{DEO10}. More precisely, the question might be independent of standard axioms of set theory. Some results have showed that some relativized versions of the $P = NP$ question are independent of reasonable formalizations of set theory \cite{HOP76}.

@@

>>>>

The $P = NP$ question is also singular in the number of approaches that researchers have brought to bear upon it over the years \cite{DEO10}. From the initial question in logic, the focus moved to complexity theory where early work used diagonalization and relativization techniques \cite{DEO10}. It was showed that these methods were perhaps inadequate to resolve $P$ versus $NP$ by demonstrating relativized worlds in which $P = NP$ and others in which $P \neq NP$ \cite{BA75}. This shifted the focus to methods using circuit complexity and for a while this approach was deemed the one most likely to resolve the question \cite{DEO10}. Once again, a negative result showed that a class of techniques known as $``$Natural Proofs$"$ that subsumed the above could not separate the classes $NP$ and $P$, provided one-way functions exist \cite{RAZ97}. There has been speculation that resolving the $P = NP$ question might be outside the domain of mathematical techniques \cite{DEO10}. More precisely, the question might be independent of standard axioms of set theory \cite{DEO10}. Some results have showed that some relativized versions of the $P = NP$ question are independent of reasonable formalizations of set theory \cite{HOP76}.

@@

For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$? In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least two consecutive pair of nodes in the sequence where they are not connected by an edge.
